### 2016-02-11 inputs/discussion.tex
fil_last

Alfalfa datasets did not present population structure \cite{Annicchiarico2015}, while rice population was intrinsically stratified - being a collection of five subpopulations. Population structure is implicitly used by algorithms like Beagle, FILLIN and KNNI, that create clusters of similar genotypes, and it is likely to affect imputation accuracy.\\
The most dramatic difference between datasets was found with FILLIN. The algorithm costantly produced 100\% uninputed results in alfalfa, while resulted in average performances in rice (albeit inferior to the other algorithms). This behaviour is probably due to FILLIN being specifically designed to target inbred lines (as the name itself indicates).

>>>>

%
%The most dramatic difference between datasets was found with FILLIN. The algorithm costantly produced 100\% uninputed results in alfalfa, while resulted in average performances in rice (albeit inferior to the other algorithms). This behaviour is probably due to FILLIN being specifically designed to target inbred lines (as the name itself indicates).
%

There was no population structure in alfalfa \cite{Annicchiarico2015}, while the rice dataset was intrinsically stratified ---being a collection of five subpopulations (\textit{indica}, \textit{temperate japonica} \textit{tropical japonica}, \textit{aus} and \textit{aromatic}). Most imputation methods implicitly exploit population structure (e.g. KNNI computes distances based on genetic relatedness; Beagle reconstructs haplotypes based on genetic similarities), without explicitly modelling it. The imputation of missing genotypes, however, is not an inferential problem such as GWAS (genome-wide association study), where the significance and estimate of SNP effects are known to be inflated if population structure is not included in the model, and the impact on the accuracy of imputation is likely to be small. In cattle from Scandinavian countries, Brondum et al \cite{brondum2012short} actually found higher imputation accuracy when combining populations (cattle breeds) in Beagle (without explicitly modelling the population structure), most likely as a result of the larger sample size. On the other hand, population stratification may help explain why FILLIN performed poorly in our rice dataset, which is a collection of subpopulations, while this algorithm is optimised for homogeneous inbred populations. 
However, the influence of population structure on the accuracy of imputation was not formally tested in this work, and this remains an interesting topic for further investigation.
